Julia for HPC: In Situ Data Analysis with Julia for Climate Simulations at Large Scale

### 2023-09-18 paper/paper.tex
Update paper.tex

\usepackage{amsmath}
%\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algorithm, algorithmic}

@@

\begin{algorithm}[t]
\small{
\textbf{Input:} EAM simulation data.\\

\textbf{Output:} A list of time steps and corresponding simulation years when SSW is detected.\\

global counter: Keeps track of consecutive negative daily zonal mean zonal wind values.\\

\For{ each EAM time\_step}
{
    \eIf{(current\_time\_step == end\_of\_day)}
    {
        Compute partial zonal mean zonal wind values at each MPI process.\\
        Compute the global zonal mean zonal wind with MPI:Reduction.\\
        \If{(global zonal mean zonal wind < 0)}
        {
            counter=counter+1\\
        }
        \If{(counter == 10)}
        {
            Record current time step as the beginning of a SSW event.\\
            counter=0\\
        }
    }
    {
        continue
    }
}
\caption{In situ algorithm for SSW detection.}
\label{ssw_algo}
}
\end{algorithm}

>>>>

\usepackage{amsmath}
%\usepackage[ruled,vlined]{algorithm2e}
%\usepackage{algorithm, algorithmic}

@@
